---
title: "Additional Results from the Systematic Review"
subtitle: "Are we getting interactions wrong? The role of link functions in psychological research"
author: "Margherita Calderan, Filippo Gambarota, Laura Sità, Tommaso Feraco, Enrico Toffalini"
format:
  html:
    theme: cosmo
    toc: true
    toc-title: "Contents"
    smooth-scroll: true
    embed-resources: true
    link-external-newwindow: true
execute:
  echo: false
  warning: false
  message: false
---

<style>
.table-heading {
  border-bottom: none;
  padding-bottom: 0;
}
</style>

## About this page

This page provides additional tables and results complementing the poster presented at the 2026 conference of the European Mathematical Psychology Group.

The materials below are drawn from a manuscript currently in preparation and not yet submitted for peer review and report additional results that could not be included in the poster due to space limitations.

```{r}
#| label: setup
#| include: false

knitr::opts_chunk$set(
  echo = FALSE,
  message = FALSE,
  warning = FALSE,
  comment = "#>"
)

# This supplement reads a few already-generated result files so that the
# printed tables reproduce exactly. The reader does not need any of these
# files: every table below degrades to a short note if its source is absent,
# and the text never asks the reader to open a repository file.
find_file <- function(...) {
  rel <- file.path(...)
  candidates <- c(rel, file.path("..", rel))
  hit <- candidates[file.exists(candidates)]
  if (length(hit) == 0) return(NA_character_)
  hit[1]
}

read_csv_if_exists <- function(...) {
  path <- find_file(...)
  if (is.na(path)) return(NULL)
  read.csv(path, stringsAsFactors = FALSE, check.names = FALSE)
}

missing_note <- function(text) {
  cat("*", text, "*\n\n", sep = "")
  invisible(NULL)
}

zap0 <- function(x, tol = 1e-8) {
  x <- as.numeric(x)
  x[!is.na(x) & abs(x) < tol] <- 0
  x
}

fmt_num <- function(x, digits = 3) {
  ifelse(is.na(x), "--", formatC(zap0(as.numeric(x)), format = "f", digits = digits))
}

fmt_percent <- function(x, digits = 1) {
  ifelse(is.na(x), "--", paste0(formatC(as.numeric(x), format = "f", digits = digits), "%"))
}

fmt_rate <- function(x, digits = 1) {
  ifelse(is.na(x), "--", paste0(formatC(100 * as.numeric(x), format = "f", digits = digits), "%"))
}

fmt_rate_ci <- function(rate, low, high, digits = 1) {
  ifelse(
    is.na(rate),
    "--",
    paste0(
      fmt_rate(rate, digits),
      " [", formatC(100 * as.numeric(low), format = "f", digits = digits),
      ", ", formatC(100 * as.numeric(high), format = "f", digits = digits), "]"
    )
  )
}

short_journal <- function(x) {
  x <- gsub("Journal of Experimental Psychology: General", "JEP: General", x, fixed = TRUE)
  x <- gsub("Journal of Personality and Social Psychology", "JPSP", x, fixed = TRUE)
  x
}

short_item <- function(x) {
  out <- x
  out[grepl("non-identity", out, ignore.case = TRUE)] <- "Uses non-identity link"
  out[grepl("Explicit link", out, ignore.case = TRUE)] <- "Explicit link reported"
  out[grepl("incorrect", out, ignore.case = TRUE)] <- "Identity link flagged"
  out[grepl("significant", out, ignore.case = TRUE)] <- "Significant flagged interaction"
  out
}

print_table_if_exists <- function(note_if_missing, ..., transform = identity, digits = 3) {
  d <- read_csv_if_exists(...)
  if (is.null(d)) return(missing_note(note_if_missing))
  d <- transform(d)
  print(knitr::kable(d, digits = digits))
  cat("\n\n")
  invisible(d)
}

include_graphic_if_exists <- function(..., note_if_missing = NULL) {
  path <- find_file(...)
  if (!is.na(path) && grepl("\\.pdf$", path) && !knitr::is_latex_output()) {
    png_alt <- sub("\\.pdf$", ".png", path)
    path <- if (file.exists(png_alt)) png_alt else NA_character_
  }
  if (is.na(path)) {
    if (is.null(note_if_missing)) note_if_missing <- "Figure not available in this build."
    return(missing_note(note_if_missing))
  }
  knitr::include_graphics(path)
}

compact_agreement <- function(d) {
  label <- if ("label" %in% names(d)) d$label else d$variable
  data.frame(
    Item = short_item(label),
    N = d$n_double_coded,
    Agreement = fmt_rate(d$agreement),
    Kappa = fmt_num(d$kappa, 2),
    `Coder 1 yes` = fmt_percent(d$coder1_yes_percent),
    `Coder 2 yes` = fmt_percent(d$coder2_yes_percent),
    check.names = FALSE
  )
}

compact_by_journal <- function(d) {
  data.frame(
    Journal = short_journal(d$journal),
    `Eligible` = d$eligible_n,
    `Interaction` = d$interaction_testing_n,
    `Interaction / eligible` = fmt_percent(d$interaction_testing_percent_of_eligible),
    `Non-identity link` = fmt_percent(d$non_identity_link_percent_interaction),
    `Explicit link` = fmt_percent(d$explicit_link_percent_interaction),
    `Identity flagged` = fmt_percent(d$incorrect_identity_percent_interaction),
    check.names = FALSE
  )
}
```

## Table 1: Screening flow {.table-heading}

```{r}
#| label: screening-flow
#| results: asis

print_table_if_exists(
  note_if_missing = "Screening-flow table not available in this build.",
  "tables", "review-screening-flow.csv",
  transform = function(d) {
    required <- c("step", "n")
    missing <- setdiff(required, names(d))
    if (length(missing) > 0) {
      stop("Screening-flow table is missing required columns: ", paste(missing, collapse = ", "), call. = FALSE)
    }
    out <- data.frame(
      Step = d$step,
      N = d$n,
      check.names = FALSE
    )
    optional_cols <- setdiff(names(d), c("step", "n"))
    for (col in optional_cols) {
      out[[col]] <- d[[col]]
    }
    out
  }
)
```

## Table 2: Coded variables and their preregistered definitions {.table-heading}

| Variable | Definition (preregistered) | Type |
|---|-------------|---|
| Tests interactions | Whether the article tests at least one interaction term in a statistical model or using an ANOVA. | Boolean |
| Uses non identity link function | Whether at least one tested interaction is presumably analyzed with a non-identity link function (for example, because a generalized linear model was used). | Boolean |
| Explicit link function | Whether the link function is explicitly declared for at least one statistical model in the article. Indicating only which generalized linear model or family was used is not enough. | Boolean |
| Incorrect identity link function | Whether at least one tested interaction is analyzed using an identity link function when another, non-identity link function would be more appropriate. | Boolean |
| Finds significant interactions | Whether at least one interaction, among those where the link was coded as incorrectly identity, yields a statistically significant result, or is considered and discussed analogously in non-frequentist analyses. | Boolean |
| Response variable types | Non-exclusive list of response-variable types on which interactions are tested (for example, sum score, accuracy, error count, response times, ordinal/Likert). | Category |

## Table 3: By-journal descriptives {.table-heading}

```{r}
#| label: by-journal
#| results: asis

print_table_if_exists(
  note_if_missing = "By-journal table not available in this build.",
  "tables", "review-by-journal.csv",
  transform = compact_by_journal
)
```

## Additional materials

- [View the presentation for the Cognitive Science Arena](https://sitalaura.github.io/link-functions/link-functions.html)
- [View the preregistration on OSF](https://osf.io/tpjax/overview?view_only=7feccf54ff484fe093cf65579617b215)

## Contact

For questions about the study, please contact:

**Laura Sità**  
[laura.sita@studenti.unipd.it](mailto:laura.sita@studenti.unipd.it) <br>
Department of General Psychology  
University of Padova